Critical Temperature of the Ising Ferromagnet on Proximity Graphs derived from Square Lattices by Site Displacement

### 2013-11-25 Tex/paper/abstract.tex
Umformulierungen, Korrketuren

I perform Monte Carlo simulations using a combination of the single spin
flip Metropolis, Wolff Cluster update and Parallel Tempering algorithms
to study determine the critical temperatures of an Ising Ferromagnet on
the Relative Neighborhood graph and Gabriel graph which are subgraphs of
the Delaunay Triangulation and proximity graphs. The graphs are derived
from square lattices which nodes are displaced by a Gaussian distributed
random variable. The coupling is set to be depended on the distance of
the nodes. The deviation of the proximity graph from a square lattice is
governed by the width of the Gaussian distribution \(\sigma\). Because
only the lattice structure and coupling is changed, it is expected that
this model lies within the square lattice Ising Ferromagnet universality
class. This expectation is confirmed.
The critical temperatures are shown to depend mainly on the average degree
and the type of the underlying proximity graph.

>>>>

Monte Carlo simulations are performed
to determine the critical temperatures of an Ising Ferromagnet on
proximity graphs Relative Neighborhood graph and Gabriel graph which are
subgraphs of the Delaunay Triangulation. The graphs are derived
from square lattices which nodes are displaced by a Gaussian distributed
random variable to the limit of a Poisson point process. The coupling is
set to be depended on the distance of
the nodes. The deviation of the proximity graph from a square lattice is
governed by the width of the Gaussian distribution \(\sigma\). Because
only the lattice structure and coupling is changed, it is expected that
this model lies within the square lattice Ising Ferromagnet universality
class. This expectation is confirmed.
The critical temperatures are shown to depend mainly on the average degree
and the type of the underlying proximity graph.
